---
title: "2019 Canadian Pacific Hake fishery"
subtitle: "`r Sys.Date()`"
author: "JTC<br/>🐟<br/>Chris Grandin"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [shinobi, ninjutsu]
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false

---


```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      error = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      results = FALSE,
                      cache = TRUE,
                      autodep = TRUE,
                      cache.comments = FALSE,
                      fig.align = "center",
                      fig.width = 8,
                      fig.height = 5,
                      dev = 'svg',
                      fig.asp = 0.618)
options(htmltools.dir.version = FALSE)
```

```{r load-libraries, message = FALSE}
library(here)
library(tidyverse)
library(gfutilities)
library(hakedata)
source(here("R/generate-data.R"))
extract_date <- Sys.Date()
year <- 2019
coastwide_tac <- 519834
canada_prop <- 0.2612
canada_tac_nocarryover <- coastwide_tac * canada_prop
carryover <- 20286
canada_tac <- canada_tac_nocarryover + carryover
landings_enddate <- lubridate::date(extract_date)
landings_to_extractdate <- 0
total_can_catch <- sum(ct_ft$landings, ct_ss$landings, ct_jv$landings) / 10e3
ft_perc <- sum(ct_ft$landings) / 10e3 / total_can_catch * 100
ss_perc <- sum(ct_ss$landings) / 10e3 / total_can_catch * 100
jv_perc <- sum(ct_jv$landings) / 10e3 / total_can_catch * 100
alloc_perc <- total_can_catch / canada_tac * 100
```

# **TAC and landed catch**

*All catch values are preliminary*

`r year` Coastwide TAC = `r gfutilities::f(coastwide_tac)` mt

Canadian TAC (`r gfutilities::f(canada_prop * 100, 2)`%) = `r gfutilities::f(canada_tac_nocarryover)` mt

Canadian carryover = `r gfutilities::f(carryover)` mt

Total Canadian TAC = `r gfutilities::f(canada_tac)` mt

Total landings up to Nov 27 = `r gfutilities::f(total_can_catch)` mt

Canadian fisheries caught `r gfutilities::f(alloc_perc, 1)`% of their TAC

Freezer trawlers caught `r gfutilities::f(ft_perc, 1)`% of Canadian catch

Shoreside caught `r gfutilities::f(ss_perc, 1)`% of Canadian catch

JV caught `r gfutilities::f(jv_perc, 1)`% of Canadian catch


---

# **Freezer trawler cumulative catch**
```{r cumu-catch-ft}
theme_set(hake_theme())
plot_cumu_catch(ct_ft, ylim = c(1, 60), horiz_line_spacing = 10)
```

---

# **Shoreside cumulative catch**
```{r cumu-catch-ss}
theme_set(hake_theme())
plot_cumu_catch(ct_ss, ylim = c(1, 60), horiz_line_spacing = 10)
```

---

# **JV cumulative catch**
```{r cumu-catch-jv}
theme_set(hake_theme())
plot_cumu_catch(ct_jv, ylim = c(1, 10))
```
